### 2014-04-14 doc/uist14/relatedwork.tex
added discussion of sources 10 and 20

\bjoern{TODO: Add discussion of ~\cite{swindells_that_2002,merrill_augmenting_2007}.}

>>>>

\claire{Other targeting systems use IR with handheld pointers ~\cite{swindells_that_2002} and as well as wearable devices such as rings and Bluetooth audio earpieces ~\cite{merrill_augmenting_2007} to connect to smart devices. Our system tackles an unresolved issue of such IR-based approaches-- navigating an area dense with potential targets. }
